---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  dev.args = list(bg = "#00000000"),
  dpi = 300
)
```

# Flametree

<!-- badges: start -->
[![R-CMD-check](https://github.com/djnavarro/flametree/workflows/R-CMD-check/badge.svg)](https://github.com/djnavarro/flametree/actions)
[![Codecov test coverage](https://codecov.io/gh/djnavarro/flametree/branch/master/graph/badge.svg)](https://codecov.io/gh/djnavarro/flametree?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/flametree)](https://CRAN.R-project.org/package=flametree)
[![CRAN RStudio mirror
downloads](https://cranlogs.r-pkg.org/badges/grand-total/flametree?color=blue)](https://r-pkg.org/pkg/flametree)
<!-- badges: end -->

Flametree provides a system for making generative art in R, written with two goals in mind. First, and perhaps foremost, art is inherently enjoyable and generative artists working in R need packages no less than any other R users. Second, the system is designed to be useful in the classroom: getting students to make artwork in class is an enjoyable exercise and flametree can be used as a method to introduce some key R concepts in a fun way. You can install the current version of flametree with:

``` r
install.packages("flametree")
```

Alternatively you can install the development version of flametree with:

``` r
# install.packages("devtools")
devtools::install_github("djnavarro/flametree")
```

Flametree is fairly flexible and produces art in several different styles. One example is shown here, other possibilities are described throughout the documentation.

```{r example, fig.width=8, fig.height=4}
library(flametree)
flametree_grow(seed = 2, trees = 3) %>% 
  flametree_plot(style = "voronoi")
```
