---
title: "Getting started"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Flametree provides a system for making generative art in R, written with two goals in mind. First, and perhaps foremost, art is inherently enjoyable and generative artists working in R need packages no less than any other R users. Second, the system is designed to be useful in the classroom: getting students to make artwork in class is an enjoyable exercise and flametree can be used as a method to introduce some key R concepts in a fun way. This article will help you get started with the package.

```{r setup}
library(flametree)
```

The flametree system has two main components: the `flametree_grow()` function generates a tidy tibble that specifies a suitable data structure, and the `flametree_plot()` function takes this tibble and creates plots using ggplot2. First we look at the data structure:

```{r make-flametree-data}
flametree_grow()
```

The output is always a tibble with the same 12 columns. Each row specifies the location of a point in the `coord_x` and `coord_y` values, and it takes three such points to define a curved line segment. Segments are arranged so that when plotted, the overall image looks a little like a tree:

```{r make-flametree-plot}
flametree_grow() %>% 
  flametree_plot()
```

## Customising the generative process

blah blah modify simple args to grow function

## Customising the plot

blah blah modify palette and background args in plot

## Saving the plot

blah blah save function

